\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-02-06 manuscript.Rmd
Analysis strategy: point by point: Semantics

We also analysed possible semantic overlap of our developed tool using "Semantic Scale Network" enginee [@rosenbusch2020semantic].  Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.

>>>>

We also analysed possible semantic overlap of our developed tool using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy. Additionally, To identify the educational grade level required to understand the items in our tool we subjected tool to Flesch-Kincaid Grade Level [@flesch1948new]

Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
